DEBS Grand Challenge: A High-Throughput, Scalable Solution for Calculating Frequent Routes and Profitability of New York Taxis

### 2015-05-13 presentation/grand_challenge.tex
fixed version

\documentclass{beamer}

@@

\begin{frame}
\frametitle{Problem Characteristics}
\begin{itemize}
	\item The whole dataset contains 173 million records within an year
	\item There are 899010 unique routes and 34 unique cells
	\item 30 minute time window contains around 10000 events assuming equal event distribution
		\begin{itemize}
			\item Thousands of route and cell details need to process with each event
		\end{itemize}
	\item Top ten frequent routes and profitable cells should be calculated whole dataset
		\begin{itemize}
                        \item Dataset can not be simply partitioned 
                \end{itemize}
\end{itemize}

@@

>>>>

\documentclass[]{beamer}

@@

\begin{frame}
\frametitle{Problem Characteristics}
\begin{itemize}
	\item The whole dataset contains 173 million records within year 2013
	\item There are 899010 unique routes and 56697 unique cells
	\item 30 minute time window contains around 10000 events assuming equal event distribution
		\begin{itemize}
			\item Thousands of route and cell details need to process with each event
		\end{itemize}
	\item Top ten frequent routes and profitable cells should be calculated whole dataset
		\begin{itemize}
                        \item Dataset can not be simply partitioned 
                \end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Profitable Cells Query}
\begin{itemize}
        \item Median fare calculation
		\begin{itemize}
			\item Use the PriorityQueue based running median algorithm
		\end{itemize}
        \item Handling empty taxis
		\begin{itemize}
                        \item Generate two events (Pickup event and Drop event) for each dataset event
                \end{itemize}
        \item Handling drop event expiration
		\begin{itemize}
                        \item Keep taxi ids within the profitable cell object
                \end{itemize}
\end{itemize}
